---
title: "Commencement Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Commencement Example}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

*Built with R 
`r getRversion()`*

***

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.height = 4,
  fig.width = 8.84,
  dev.args = list(bg = "#222222"),
  dev = "CairoSVG",
  fig.ext = "svg"
)
library(knitr)
library(receptiviti)
library(lingmatch)
library(splot)
options(splot.dark = TRUE)
```

This example uses the `Receptiviti` API to analyze commencement speeches.

## Data

We'll start by collecting and processing the speeches.

### Collection

The speeches used to be provided more directly, but the service hosting them has since shut down.

They are still available in a slightly less convenient form,
as the source of a site that displays them:
[whatrocks.github.io/commencement-db](https://whatrocks.github.io/commencement-db).

First, we can retrieve metadata from a separate repository:

```{r}
speeches <- read.csv(paste0(
  "https://raw.githubusercontent.com/whatrocks/markov-commencement-speech",
  "/refs/heads/master/speech_metadata.csv"
))

library(knitr)
kable(speeches[1:5, 2:4])
```

One file in the source repository contains an invalid character on Windows (`:`),
so we'll need to pull them in individually, rather than cloning the repository:

```{r}
text_dir <- "../../commencement_speeches/"
dir.create(text_dir, FALSE)

text_url <- paste0(
  "https://raw.githubusercontent.com/whatrocks/commencement-db",
  "/refs/heads/master/src/pages/"
)
for (file in speeches$filename) {
  out_file <- paste0(text_dir, sub(":", "", file, fixed = TRUE))
  if (!file.exists(out_file)) {
    text <- readLines(paste0(
      text_url, sub(".txt", "/index.md", file, fixed = TRUE)
    ), warn = FALSE)
    writeLines(
      text[-seq_len(max(grep("^---", text)) + 1)],
      out_file
    )
  }
}
```

### Text Preparation

Now we can read in the texts and associate them with their metadata:

```{r}
speeches$text <- vapply(speeches$filename, function(file) {
  paste(readLines(paste0(
    text_dir, sub(":", "", file, fixed = TRUE)
  ), warn = FALSE), collapse = " ")
}, "")
```

The texts contain a few special characters, which we can replace:

```{r}
# general special character replacement
library(lingmatch)
clean <- lma_dict(special, as.function = gsub)
speeches$text <- clean(speeches$text)

# ensure list items are treated as separate sentences
speeches$text <- gsub("([a-z]) •", "\\1. ", speeches$text)
```

## Analyze Full Texts

We might start by seeing if any speeches stand out in terms of language style,
or if there are any trends in content over time.

### Load Package

If this is your first time using the package, see the
[Get Started](https://receptiviti.github.io/receptiviti-r/articles/receptiviti.html)
guide to install it and set up your API credentials.

```{r}
library(receptiviti)
```

### Process Text

Now we can send the texts to the API for scoring, and join the results we get to
the metadata:

```{r}
# since our texts are from speeches,
# it might make sense to use the spoken norming context
processed <- receptiviti(speeches$text, version = "v2", context = "spoken")
processed <- cbind(speeches[, 1:4], processed)

kable(processed[1:5, -(1:7)], digits = 3, row.names = FALSE)
```

### Analyze Style

To get at stylistic uniqueness, we can calculate Language Style Matching
between each speech and the mean of all speeches:

```{r}
# Currently, the lingmatch package only automatically handles
# `liwc.` prefixes, so we'll rename the `liwc15.` ones.
colnames(processed) <- sub("liwc15", "liwc", colnames(processed), fixed = TRUE)

processed$lsm_mean <- lingmatch(processed, mean, type = "lsm")$sim

kable(processed[
  order(processed$lsm_mean)[1:10],
  c("name", "school", "year", "lsm_mean", "summary.word_count")
], digits = 3, row.names = FALSE)
```

Here, it is notable that the most stylistically unique speech was delivered in
American Sign Language, and the second most stylistically unique speech was
a short rhyme.

We might also want to see which speeches are most similar to one another:

```{r}
# calculate all pairwise comparisons
lsm_pairs <- lingmatch(processed, type = "lsm", symmetrical = TRUE)$sim

# set self-matches to 0
diag(lsm_pairs) <- 0

# identify the closest match to each speech
speeches$match <- max.col(lsm_pairs, "last")
best_match <- lsm_pairs[
  speeches$match + (seq_len(nrow(lsm_pairs)) - 1) * nrow(lsm_pairs)
]

# look at the top matches
top_matches <- order(-best_match)[1:20]
top_matches <- data.frame(a = top_matches, b = speeches[top_matches, "match"])
top_matches <- top_matches[!duplicated(apply(
  top_matches, 1, function(pair) paste(sort(pair), collapse = "")
)), ]
kable(data.frame(
  speeches[top_matches$a, 2:4],
  Similarity = best_match[top_matches$a],
  speeches[top_matches$b, 2:4],
  check.names = FALSE
), digits = 3, row.names = FALSE)
```

### Analyze Content

To look at content over time, we might focus on a potentially interesting framework,
such as drives:

```{r, fig.alt="drives categories over time"}
# select drives categories
drives <- grep("drives", colnames(processed), value = TRUE, fixed = TRUE)

# identify those more correlated with time (excluding the few earliest cases)
later_times <- processed$year > 1980
trending_drives <- drives[order(-abs(cor(
  processed[later_times, drives], processed$year[later_times]
)))[1:3]]

splot(
  scale(processed[, trending_drives]) ~ year, processed, year > 1980,
  title = FALSE, laby = "Score", lpos = "top"
)
```

To better visualize the effects, we might look between aggregated blocks of time:

```{r, fig.alt="drives categories between time periods"}
time_median <- median(processed$year)
processed$time_period <- paste(c("<", ">="), time_median)[
  (processed$year >= time_median) + 1
]

splot(
  scale(processed[, trending_drives]) ~ time_period, processed,
  title = FALSE, laby = "Score", lpos = "top"
)
```

This suggests that references to risk and reward have increased since the 2000s while references
to power have decreased at a similar rate. (Note that error bars represent how much variance there
is within groups, which allows you to eyeball the statistical significance of mean differences.) 

The shift in emphasis from power to risk-reward could reflect that commencement speakers are now
focusing more abstractly on the potential benefits and hazards of life after graduation, whereas
earlier speakers more narrowly focused on ambition and dominance (perhaps referring to power held
by past alumni and projecting the potential for graduates to climb social ladders in the future).
You could examine a sample of speeches that show this pattern most dramatically (speeches high in
risk-reward and low in power in recent years, and vice versa for pre-2009 speeches) to help
determine how these themes have shifted and what specific motives or framing devices seem to
have been (de)emphasized.

## Analyze Segments

Another thing we might look for is trends within each speech.
For instance, are there common emotional trajectories over the course of a speech?

One way to look at this would be to split texts into roughly equal sizes,
and score each section:

```{r}
# split texts into 3 segments each, keeping sentences together
segmented_text <- read.segments(
  text = speeches$text, segment = 3, bysentence = TRUE
)
segmented_text <- cbind(speeches[segmented_text$input, 1:4], segmented_text)

kable(segmented_text[1:9, 2:7], row.names = FALSE)
```

### Process Text

Now we can send each segment to the API to be scored:

```{r}
processed_segments <- receptiviti(
  segmented_text$text,
  version = "v2", context = "spoken"
)
segmented_text <- cbind(segmented_text, processed_segments)

kable(segmented_text[1:9, -(1:10)], digits = 3, row.names = FALSE)
```

### Analyze Scores

The [SALLEE framework](https://docs.receptiviti.com/frameworks/emotions)
offers measures of emotions, so we might see which categories deviate
the most in any of their segments:

```{r}
# select the narrower SALLEE categories
emotions <- segmented_text[, grep("^sallee", colnames(segmented_text))[-(1:6)]]

# make contrasts for each segment
contrasts <- matrix(
  rep_len(c(1, 0, 0, 0, 1, 0, 0, 0, 1), nrow(segmented_text) * 3),
  ncol = 3, byrow = TRUE
)

# correlate emotion scores with contrasts
segment_deviations <- abs(cor(emotions, contrasts))

# select the 5 most deviating emotions
most_deviating <- segmented_text[, names(sort(-apply(
  segment_deviations, 1, max
))[1:5])]
```

Now we can look at those categories across segments:

```{r, fig.alt="SALLEE scores by segment"}
library(splot)
splot(
  most_deviating ~ segment, segmented_text,
  laby = "Score", title = FALSE, mv.as.x = TRUE, type = "bar"
)
```

The bar chart displays original values, which offers the clearest view of how meaningful the
differences between segments might be, in addition to their statistical significance
(which offers a rough guide to the reliability of differences, based on the variance within
and between segments). By looking at the bar graph, you can immediately see that admiration shows
some of the starkest differences between middle and early/late segments.

```{r, fig.alt="scaled SALLEE scores by segment"}
splot(
  scale(most_deviating) ~ segment, segmented_text,
  leg = "out", laby = "Score (Scaled)", title = FALSE, prat = c(4, 1)
)
```

The line charts, on the other hand, shows standardized values, effectively zooming in on the
differences between segments. This more clearly shows, for example, that admiration and joy
seem to be used as bookends in commencement speeches, peaking early and late, whereas more negative
and intense emotions such as anger, disgust, and surprise peak in the middle section.
